---
output:
  
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
        
  pdf_document:
    fig_caption: true
    fig_crop: false
  word_document: default
params:
    printcode: false
---

---
title: "MACHINE LEARNING ASSIGNMENT-4"
author: "RAHUL_R"
Reg No: "1P23CS027"
date: "2024-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r  include=FALSE}
library(ISLR)
library(MASS)
library(boot)
```

# QUESTION 1

### a. Using the summary() and glm() functions, determine the estimated standard errors for the coefficients associated with income and balance in a multiple logistic regression model that uses both predictors.
```{r}
fit <- glm(default ~ income + balance, data = Default, family = "binomial")
summary(fit)
```
After seeing the summary balance has high standard error 2.274e-04 and income has small compare to balance 4.985e-06


### b. Write a function, `boot.fn()`, that takes as input the `Default` data set  as well as an index of the observations, and that outputs the coefficient estimates for `income` and `balance` in the multiple logistic regression   model.


```{r}
boot.fn=function(data,index){
  q_b.fit=glm(default~income+balance,data=data,family = binomial,subset = index)
  return(coef(q_b.fit))
}
```


### c. Use the `boot()` function together with your `boot.fn()` function to   estimate the standard errors of the logistic regression coefficients for income and balance.

```{r}
set.seed(1)
boot(Default,boot.fn,100)
```
### d. Comment on the estimated standard errors obtained using the `glm()` function and using your bootstrap function.

Overall, the bootstrap results show that the model coefficients are reasonably stable, with low `standard errors`, indicating reliable estimates.



# QUESTION 2

### a. Fit a logistic regression model that predicts `Direction` using `Lag1` and `Lag2`.

```{r}
fit <- glm(Direction ~ Lag1 + Lag2, data = Weekly, family = "binomial")
```

### b. Fit a logistic regression model that predicts `Direction` using `Lag1` and`Lag2` using all but the first observation_.
```{r}
q2_fit2 <- glm(Direction ~Lag1 + Lag2,data = Weekly[-1, ],family = "binomial" )
```

### c. Use the model from (b) to predict the direction of the first   observation. You can do this by predicting that the first observation will go up if $P($`Direction="Up" | Lag1 , Lag2`$)  0.5$. Was this observation correctly classified?

```{r}
predict(q2_fit2, newdata = Weekly[1, , drop = FALSE], type = "response")  >0.5
```
Yes the observation was correctly classified.

### d. Write a for loop from $i = 1$ to $i = n$, where $n$ is the number of observations in the data set, that performs each of the following steps:
    i.   Fit a logistic regression model using all but the $i$th observation
         to predict `Direction` using `Lag1` and `Lag2` .
    ii.  Compute the posterior probability of the market moving up
         for the $i$th observation.
    iii. Use the posterior probability for the $i$th observation in order
         to predict whether or not the market moves up.
    iv.  Determine whether or not an error was made in predicting the
         direction for the $i$th observation. If an error was made, then
         indicate this as a 1, and otherwise indicate it as a 0.

```{r}
error <- numeric(nrow(Weekly))
for (i in 1:nrow(Weekly)) {
  fit <- glm(Direction ~ Lag1 + Lag2, data = Weekly[-i, ], family = "binomial")
  p <- predict(fit, newdata = Weekly[i, , drop = FALSE], type = "response") > 0.5
  error[i] <- ifelse(p, "Down", "Up") == Weekly$Direction[i]
}
(total_errors <- sum(error))
```

### e. Take the average of the $n$ numbers obtained in (d) in order to obtain the LOOCV estimate for the test error. Comment on the results.

```{r}
mean(error)
```
